\PaperTitle

### 2024-05-05 Final_Report/paper.tex
Added grid search section into RF

>>>>

Within random forest models, many hyperparameters can be fine tuned to optimize the model. For this project, we chose to optimize the hyperparameters for n estimators (number of trees in the forest), 
max depth (maximum depth (levels) in the tree), and min samples split (minimum samples within a node to be able to split it into children). In order to optimize all of these hyperparameters, we used a grid search to find the best combination of hyperparameters that would 
yield the highest accuracy. Within the grid search, we also employed the cross validation technique of Kfold validation, which divides the training data into k number of folds. This process is repeated k times, with each fold being used as the validation set exactly once. The results from each fold are then averaged to produce a single estimation of model performance. Overall, after running for many different combinations of values for the 
hyperparameters, the ones we decided to utilize, based on the highest test accuracy scores, were n estimators = 100, max depth = 13, and min samples split = 5.
